Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-16 latex/tex/experiments.tex
to 10 pages

\begin{figure}
\begin{center}
\includegraphics[height=2in, width=\columnwidth]{plots/dc_hierarchical_speedup.pdf}
\caption{Strong Scaling for Clustering on \hyper{}}
\label{fig:dcspeedup}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/synthetic_rank2_speedup.pdf}
\caption{Synthetic Data}
\label{fig:synrank2speedup}
\end{center}
\end{subfigure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/realworld_rank2_speedup.pdf}
\caption{\image{} Data}
\label{fig:rwrank2speedup}
\end{center}
\end{subfigure}
\caption{Strong Scaling Speedup for Rank-2 NMF}
\label{fig:rank2speedup}
\end{figure}

@@

From \Cref{eq:treecost}, we expect to see perfect strong scaling in a computationally bound hierarchical clustering problem with target cluster count $k=100$.
As $k$ is large, we expect the latency cost of small problems deep in the tree to limit scalability.

@@

\begin{figure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/synthetic_hierarchical_speedup.pdf}
\caption{Synthetic Data}
\label{fig:synhierspeedup}
\end{center}
\end{subfigure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/realworld_hierarchical_speedup.pdf}
\caption{\image{} Data}
\label{fig:rwhierspeedup}
\end{center}
\end{subfigure}
\caption{Strong Scaling Speedup for Clustering}
\label{fig:rank2speedup}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/dc_hierarchical_speedup.pdf}
\caption{Strong Scaling for Clustering on \hyper{}}
\label{fig:dcspeedup}
\end{center}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/synthetic_rank2_speedup.pdf}
\caption{Synthetic Data}
\label{fig:synrank2speedup}
\end{center}
\end{subfigure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/realworld_rank2_speedup.pdf}
\caption{\image{} Data}
\label{fig:rwrank2speedup}
\end{center}
\end{subfigure}
\caption{Strong Scaling Speedup for Rank-2 NMF}
\label{fig:rank2speedup}
\end{figure}

@@

From \Cref{eq:treecost}, we expect to see perfect strong scaling in a computationally bound clustering problem with target cluster count $k=100$.
As $k$ is large, we expect the latency cost of small problems deep in the tree to limit scalability.

@@

\begin{figure}
\centering
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/synthetic_hierarchical_speedup.pdf}
\caption{Synthetic Data}
\label{fig:synhierspeedup}
\end{center}
\end{subfigure}
\begin{subfigure}{1.5in}
\begin{center}
\includegraphics[height=1.4in, width=1.4in]{plots/realworld_hierarchical_speedup.pdf}
\caption{\image{} Data}
\label{fig:rwhierspeedup}
\end{center}
\end{subfigure}
\caption{Strong Scaling Speedup for Clustering}
\label{fig:rank2speedup}
\end{figure}
